---
title: "Interneuron Analysis"
author: "Natalie Elphick"
date: "12/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 10,
                      fig.height = 8)
library(tidyverse)
library(Seurat)
library(kableExtra)
library(future)
library(clustree)
plan()
plan("multicore", workers = 4,future.seed=TRUE)
set.seed(423)
```

```{r load}

interneurons <- readRDS("../../data/interneurons_kb.rds")

```


```{r}
DefaultAssay(interneurons) <- "RNA"

interneurons = FindVariableFeatures(interneurons, selection.method = "vst", nfeatures = 10000)
all.genes = rownames(interneurons)
interneurons = ScaleData(interneurons, features = all.genes)

interneurons = RunPCA(interneurons, features = VariableFeatures(object = interneurons))


interneurons = RunUMAP(interneurons, reduction = "pca", dims = 1:30)
interneurons= FindNeighbors(interneurons, reduction = "pca", dims = 1:30)


interneurons = FindClusters(interneurons, resolution = .7)

DimPlot(interneurons, reduction = "umap", label = TRUE, repel = TRUE,pt.size = 1)
DimPlot(interneurons, reduction = "umap", label = TRUE, repel = TRUE, group.by = "timepoint",pt.size = 1)

pre.critical <- unique(interneurons@meta.data["timepoint"]) %>% pull(timepoint) 

pre.critical <- pre.critical[0:5]

interneurons@meta.data <- interneurons@meta.data %>%
  mutate(timepoint2 = ifelse(timepoint %in% pre.critical,
                             "E14-P5",
                             "P7-Adult"))


DimPlot(interneurons, reduction = "umap", label = TRUE, repel = TRUE,pt.size = 1, group.by =  "timepoint2")
```
```{r}
DimPlot(interneurons, reduction = "umap", label = TRUE, repel = TRUE, split.by =  "timepoint2",pt.size = 1)

```

```{r}
DefaultAssay(interneurons) <- "RNA"

all.markers <- FindAllMarkers(interneurons,only.pos = TRUE,logfc.threshold = 0.25)

sig.markers <- all.markers %>%
  filter(p_val_adj < 0.05) 


sig.markers %>% 
  group_by(cluster) %>%
  top_n(n = 5,wt = avg_log2FC) %>% 
  kbl() %>%
  kable_minimal()
write_csv(sig.markers, file = "sig_markers_1.csv")
```

```{r}
table(Idents(interneurons)) %>% kbl(col.names = c("Cluster","Cell Count")) %>% kable_minimal()

interneurons[["percent.olf"]] <- PercentageFeatureSet(interneurons, pattern = "^Olfr")
interneurons[["percent.vmn"]] <- PercentageFeatureSet(interneurons, pattern = "^Vmn")

FeaturePlot(interneurons,features = "percent.olf",label = TRUE, repel = TRUE, min.cutoff = "q10", max.cutoff = "q90",pt.size = 1,split.by="timepoint2")
FeaturePlot(interneurons,features = "percent.vmn",label = TRUE, repel = TRUE, min.cutoff = "q10", max.cutoff = "q90",pt.size = 1,split.by="timepoint2")
